A highly-available move operation for replicated trees

### 2019-06-17 paper/move-op.tex
paper: more on Section 5

Isabelle/HOL's can extract executable Haskell, OCaml, Scala, and Standard ML code from HOL definitions using a code generation mechanism.
However,  care must be taken when using this mechanism, as:
\begin{enumerate}
\item
The mechanism is \emph{partial} in the sense that not all HOL definitions can be realised in an executable form.
Definitions making essential use of choice principles (such as our \isa{get\_parent} function) are obvious examples of definitions that will cause problems.
However, \emph{inductively defined} relations characterised by a series of introduction rules, such as our \isa{ancestor} relation are also problematic for the code generator as making them executable necessarily requires Prolog-like proof search and mode inference.
\item
Unsophisticated use of the code generator often leads to inefficient target language code.
This is especially true when using HOL's \isa{set} type, a type of potentially infinite mathematical sets.
Whilst convenient for theorem proving purposes, this type often leads to gross inefficiency in the extracted code.
\end{enumerate}

Because of these problems, we produce

>>>>

Isabelle/HOL can generate executable Haskell, OCaml, Scala, and Standard ML code from HOL definitions using a code generation mechanism~\cite{XXX}.
However,  care must be taken when using this mechanism, as:
\begin{enumerate}
\item
The mechanism is \emph{partial} in the sense that not all HOL definitions can be realised in an executable form.
Definitions making essential use of choice principles (such as our \isa{get\_parent} function) are obvious examples of definitions that will cause problems.
However, \emph{inductively defined} relations characterised by a series of introduction rules, such as our \isa{ancestor} relation are also problematic for the code generator as making them executable necessarily requires Prolog-like proof search and mode inference.
\item
Unsophisticated use of the code generator often leads to inefficient target language code.
This is especially true when using HOL's \isa{set} type, a type of potentially infinite mathematical sets.
Whilst convenient for theorem proving purposes, this type often leads to gross inefficiency in the extracted code.
\end{enumerate}

As a result, prior to evaluating our algorithms in a real-world setting, we first produce a series of refined definitions that are optimised for efficient execution rather than ease of theorem proving.
Within these definitions, we eschew the HOL \isa{set} type, and instead use a more efficient hash-map implementation provided by the Isabelle Collections Framework~\cite{XXX}.
Using an explicit \emph{simulation relation}, we show the correctness of these efficient algorithms taking our abstract algorithms as ground truth of the correct behaviour.
Moreover, we show that our correctness theorems, such as \isa{apply\_ops\_acyclic}, easily transfer to the more efficient implementations.
